Accelerating adaptive ultrasound algorithms using graphics processing units \vspace{0.5cm}

### 2014-04-22 ThesisJP/Background/background.tex
Changes summary section in Background chap.

\section{Concluding remarks}
All the presented problems in this chapter, except DAS beamforming, have in common that they require a processing throughput of more than ten GFLOPS. Comparing this to the typical clock frequency of modern CPUs at 3 GHz we see that GFLOPS problems will require parallel execution in order to achieve real-time performance. With CPU threads the theoretical peak performance on an eight-core CPU increases to 24 GFLOPS. However, to reach a peak performance above 100 GFLOPS, SIMD instructions on a CPU or SIMT instructions on a GPU have to be used. It also must be possible to divide the problem into a large number of independent calculations.

>>>>

\section{Concluding remarks}
All the presented problems in this chapter, except DAS beamforming, have in common that they require a processing throughput in order of GFLOPS. Comparing this to the typical clock frequency of modern CPUs at 3 GHz we see that GFLOPS problems will require parallel execution in order to achieve real-time performance. With CPU threads the theoretical peak performance on an eight-core CPU increases to 24 GFLOPS. However, to reach a peak performance above 100 GFLOPS, SIMD instructions on a CPU or SIMT instructions on a GPU have to be used. It also must be possible to divide the problem into a large number of independent calculations.
